---
title: "Test file"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(skimr)
library(janitor)
```

### Data description

#### Turnover

```{r}
turnover <- read.csv("ANZ_IND_Turnover.csv")
turnover <- clean_names(turnover)
```

pers_no
action_type
reason_for_action
co_cd
company_code
personell_area
cost_ctr_code
cost_center
organizational_unit
date
turnover
turn_abs

```{r}
skim(turnover)
```

1. Cleaning change the hiring to hire employee
```{r}
turnover %>%
  count(action_type)
```
```{r}
turnover %>%
  count(organizational_unit, sort = TRUE)
```

```{r}
turnover %>%
  count(reason_for_action, sort = TRUE)
```
Add other for reason for action

2. Change the turnover column

#### Termination Data

```{r}
termination <- read.csv("ANZ_IND_Termination Data.csv")
termination <- clean_names(termination)
```

Same data but includes more terminations, have to add it to the turnover

#### Headcount Data

```{r}
headcount <- read.csv("Headcount Filtered.csv")
headcount <- clean_names(headcount)
```

```{r}
headcount2 <- read.csv("Headcount Report APAC_MAY 2019.csv")
headcount2 <- clean_names(headcount2)
```

```{r}
headcount3 <- read.csv("Headcount Filtered Connors.csv")
headcount3 <- clean_names(headcount3)
```

Add all the data tables together, remove insignificant columns 

#### New Starter Data

```{r}
new_starter <- read.csv("ANZ_IND_New Starter Data.csv")
new_starter <- clean_names(new_starter)
```

```{r}
new_starter %>%
  count(action_type)
```
```{r}
new_starter %>%
  count(reason_for_action)
```