---
title: "Test file"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(skimr)
```

### Data description

Absenteeism AND Overtime SUMMARISED
Absenteeism AND Overtime
ANZ_IND_Absenteism
All those three deal with data that has to do with absenteism or overtime

```{r}
abs_over_sum <- read.csv("Absenteeism AND Overtime SUMMARISED.csv")
abs_over <- read.csv("Absenteeism AND Overtime.csv")
abs <- read.csv("ANZ_IND_Absenteism.csv")
```

#### ANZ_IND_Absenteism

Pers.no. - individual number of the employee that was absent
A.AType - ???
Attendance.or.Absence.Type - Type of leave
Absence.Start.date - the start of the leave (change into date format)
Absence.End.date - the day that employee returned (change into date format)
Hrs - hours that employee wasnt at work (change into numeric)
Days - number of days that the employee was absent
DailyHrs - daily number of working hours
Personnel.Area - the location
Personnel.Subarea - smaller location
Position - job position
Cost.ctr - ???
Cost.Center - ???
Organizational.Unit - unit that was affected by the absentee?
Date - ??? DOB??

#### Absenteeism AND Overtime

#### Absenteeism AND Overtime SUMMARISED




			